Characterizing Signal Loss in the 21\,cm Reionization Power Spectrum: \\A Revised Study of PAPER-64

### 2018-09-20 PAPER.tex
made small adrian edits

The power spectrum results for this model are shown in Figure \ref{fig:toy_sigloss7}, and as 
expected there is a much larger amount of signal loss for this time-averaged dataset since we do a worse job estimating the true covariance. In addition, as a result of having fewer independent samples, we obtain an estimate with more scatter. This is evident by noticing that the 
green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the uniform-weighted EoR power spectrum (red). It is worth noting that a hybrid method, where the empirical covariance is calculated using the original dataset (not fringe-rate filtered) but applied to the filtered dataset, results in less loss than what is exhibited in Figure \ref{fig:toy_sigloss7} (though still lossy). This approach is worth exploring in future work; however in this paper we focus solely on ways to calculate and minimize loss associated with weighting a dataset based on itself (rather than weights associated with a dataset produced by a separate analysis).

@@

It is important to note that our signal injection methodology for assessing loss makes the assumption that we know the true signal's strength and structure. Realistically, these details about the EoR signal are unknown, and therefore our signal loss framework is subject to bias. Therefore, while this paper employs this methodology as an example of one way of estimating loss, Kolopanis et al. (\textit{in prep.}) use uniform weightings in order to produce more trustworthy, straightforward power spectrum limits that do not suffer from loss.

@@

Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second 
bootstrapping step along time entirely and now simply bootstrap over the baseline axis. Power spectrum $2\sigma$ errors (computed from bootstrap variances) with this bootstrapping change for a fringe-rate filtered noise simulation are shown in Figure 
\ref{fig:data_errors}. The estimates are uniformly weighted in order to disentangle the effects of bootstrapping from signal loss. As 
shown in the figure, when more elements are drawn for each bootstrap than the number of 
independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits (gray) below the predicted noise level (green). Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the limits (black) are shown to agree with the analytic prediction for noise. While Figure \ref{fig:data_errors} implies that errors are underestimated by a factor of $\sim$ $5$ in mK$^{2}$ for the noise simulation (whose creation details are outlined in the next section), in practice this factor is lower for the case of real data (a factor of $\sim$ $3$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.

@@

Power spectrum results for the noise simulation, which uses our full power spectrum pipeline, are shown in Figure 
\ref{fig:ps_noise}. We highlight that the bootstrapped data (black and gray points, with $2\sigma$ error bars) and thermal noise prediction (solid green) show good agreement, as bootstrapping provides an accurate estimate of the noise variance. However, the limits from the full signal loss framework (weighted and unweighted in red and blue, respectively) are inflated, likely due to the additional inclusion of sample variance that comes from the EoR simulations. While the noise simulation provides an important indicator about the accuracy of our theoretical noise calculation, we note that the calculation did not take into account additional sources of error associated with earlier analysis steps (for example, \citet{trott_wayth_2017} show how calibration specifically can add errors to visibilities). We therefore interpret our noise prediction as the sensitivity floor for our measurements.

>>>>

The power spectrum results for this model are shown in Figure \ref{fig:toy_sigloss7}, and as 
expected there is a much larger amount of signal loss for this time-averaged dataset since we do a worse job estimating the true covariance. In addition, as a result of having fewer independent samples, we obtain an estimate with more scatter. This is evident by noticing that the 
green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the uniform-weighted EoR power spectrum (red). %It is worth noting that a hybrid method, where the empirical covariance is calculated using the original dataset (not fringe-rate filtered) but applied to the filtered dataset, results in less loss than what is exhibited in Figure \ref{fig:toy_sigloss7} (though still lossy). This approach is worth exploring in future work; however in this paper we focus solely on ways to calculate and minimize loss associated with weighting a dataset based on itself (rather than weights associated with a dataset produced by a separate analysis).

@@

It is important to note that our signal injection methodology for assessing loss makes the assumption that we know the true signal's strength and structure. Realistically, these details about the EoR signal are unknown and our signal loss framework is limited by our simulations. Therefore, while this paper employs this methodology as an example of one way of estimating loss, Kolopanis et al. (\textit{in prep.}) use uniform weightings in order to produce more trustworthy, straightforward power spectrum limits that do not suffer from loss.

@@

Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second 
bootstrapping step along time entirely and now simply bootstrap over the baseline axis. Power spectrum $2\sigma$ errors (computed from bootstrap variances) with and without this bootstrapping change for a fringe-rate filtered noise simulation are shown in Figure 
\ref{fig:data_errors} in black and gray, respectively. The estimates are uniformly weighted in order to disentangle the effects of bootstrapping from signal loss. As 
shown in the figure, when more elements are drawn for each bootstrap than the number of 
independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits (gray) below the predicted noise level (green). Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the limits (black) are shown to agree with the analytic prediction for noise. While Figure \ref{fig:data_errors} implies that errors, computed prior to our bootstrapping change (gray), are underestimated by a factor of $\sim$ $5$ in mK$^{2}$ for the noise simulation (whose creation details are outlined in the next section), in practice this factor is lower for the case of real data (a factor of $\sim$ $3$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.

@@

Power spectrum results for the noise simulation, which uses our full power spectrum pipeline, are shown in Figure 
\ref{fig:ps_noise}. We highlight that the bootstrapped data (black and gray points, with $2\sigma$ error bars) and thermal noise prediction (solid green) show good agreement, as bootstrapping provides an accurate estimate of the noise variance. However, the limits from the full signal loss framework (weighted and unweighted in red and blue, respectively) are inflated, likely due to the additional inclusion of sample variance that comes from the EoR simulations. While the noise simulation provides an important indicator about the accuracy of our theoretical noise calculation, we note that the calculation did not take into account additional sources of error associated with earlier analysis steps (for example, \citet{trott_wayth_2017} show how calibration specifically can add errors to visibilities). Additionally, we recommend that future work investigate possible error correlations between baseline pairs and any interaction effects between signal and noise that may effect error calculations. Because of these reasons, we therefore interpret our noise prediction as the sensitivity floor for our measurements.
